### 2019-02-26 README.Rmd
Tweak README

Not to worry, just do as it says and run `cites_db_download()`.  This will
fetch the most recent database from online.  Currently this is test data that
is approximately 80MB.  It will expand to over 400MB in the database and during
the import proccess up to 1GB of disk space may be used temporarily.

Once you fetch the data you can connect to the database with the `cites_db()`
command.  If you have the **dplyr** package installed, you can use the
`cites_shipments()` command to load a remote `tibble()`.  You can use this
to analyze CITES data without ever loading it into memory:

>>>>

Not to worry, just do as it says and run `cites_db_download()`.  This will
fetch the most recent database from online.  Currently this is test data that
is approximately 80MB.  It will expand to over 400MB in the database. During
up to 1GB of disk space may be used temporarily.

Once you fetch the data you can connect to the database with the `cites_db()`
command.  If you have the **dplyr** package installed, you can use the
`cites_shipments()` command to load a remote `tibble` that is backed by the
database but not loaded into R.  You can use this
to analyze CITES data without ever loading it into memory, then gather your
results with `collect()`:
